### 2021-08-13 paper/paper.tex
Remove parens as sentence makes no sense without
Introduce MHD abbreviation also in the main text (before it was only introduced in the feature list, where it is also required but might be overlooked)

We compare the performance of FLUXO and \trixi for two smooth nonlinear problems,
a manufactured solution for the 3D compressible Euler equations and Alfv\'{e}n wave propagation for
the 3D ideal MHD equations~\cite{gassner2009,altmann2012}. These initial conditions, available in FLUXO and
\trixi, are typically used for the purpose of demonstrating the high-order accuracy and convergence properties
of the frameworks.

@@

To assess the performance of the two codes, we vary the polynomial degree
(\lstinline{polydeg}) from 3 to 15.
This corresponds to considering DG approximations of (increasing) spatial accuracy, from fourth up to sixteenth order.
The metric we use to analyze and compare FLUXO and \trixi simulations is a performance index (PID) that
measures the time required to advance a single degree of freedom (DOF) from one stage of the explicit Runge-Kutta
time integration scheme to the next. It is computed as
\begin{equation}
\label{eqn:pid}
\text{PID} = \frac{\text{wall-clock time}}{\#\text{time steps}\cdot 5\cdot\#\text{elements}\cdot(\text{\lstinline{polydeg}}+1)^3},
\end{equation}
where $5$ is the number of Runge-Kutta stages per time step for the selected time-stepping method. In other words, the PID acts
as a metric for the run time required for the right hand side (RHS) evaluation of each DOF.

>>>>

We compare the performance of FLUXO and \trixi for two smooth nonlinear problems,
a manufactured solution for the 3D compressible Euler equations and Alfv\'{e}n wave propagation for
the 3D ideal magnetohydrodynamics (MHD) equations~\cite{gassner2009,altmann2012}. These initial conditions, available in FLUXO and
\trixi, are typically used for the purpose of demonstrating the high-order accuracy and convergence properties
of the frameworks.

@@

To assess the performance of the two codes, we vary the polynomial degree
(\lstinline{polydeg}) from 3 to 15.
This corresponds to considering DG approximations of increasing spatial accuracy, from fourth up to sixteenth order.
The metric we use to analyze and compare FLUXO and \trixi simulations is a performance index (PID) that
measures the time required to advance a single degree of freedom (DOF) from one stage of the explicit Runge-Kutta
time integration scheme to the next. It is computed as
\begin{equation}
\label{eqn:pid}
\text{PID} = \frac{\text{wall-clock time}}{\#\text{time steps}\cdot 5\cdot\#\text{elements}\cdot(\text{\lstinline{polydeg}}+1)^3},
\end{equation}
where $5$ is the number of Runge-Kutta stages per time step for the selected time-stepping method. In other words, the PID acts
as a metric for the run time required for the right hand side (RHS) evaluation of each DOF.
